Analysis and figures

### 2025-02-17 Analysis.qmd
Figure detail work

  ggplot() +
  geom_col(aes(x = Year, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("aquamarine4", "gray65")) +
  scale_y_continuous(expand = c(0,0), limits = c(0, 65)) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        legend.position = "bottom", 
        axis.text = element_text(size = 12),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank(),
        axis.title = element_text(size = 12), 
        legend.text = element_text(size = 12),
        strip.text.x = element_text(size = 12)) +
  facet_grid(cols = vars(Strata), scales = "free_x", switch = "x")
plot_reviewCoverage
ggsave(plot = plot_reviewCoverage, "Figures/CoveragePlot.jpeg",
       width = 8, height = 4)
```

@@

sheet_Objectives |>
  separate_longer_delim(`Authorship categories`, delim = ", ") |>
  summarise(nPer = n(),
            .by = `Review ID`) |>
  summarise(AffilCount = n(),
            .by = nPer) (92-34)/92

@@

  ggplot(aes(x = Category, y = Covariates)) +
  geom_jitter(aes(colour = Category, shape = Outlier), 
              alpha = 0.3, size = 2.5,
              width = 0.25, height = 0) +
  geom_boxplot(aes(fill = Category), 
               outliers = FALSE, alpha = 0.3, colour = "gray60") +
  scale_fill_manual("", labels = c("Environmental covariates", "Structural covariates"),
                    values = c("aquamarine4", "plum4")) +
  scale_colour_manual("", labels = c("Environmental covariates", 
                                     "Structural covariates"),
                      values = c("aquamarine4", "plum4")) +
  scale_shape_manual("", labels = c("",""), 
                     limits = c(TRUE, FALSE), values = c(17, 16)) +
  scale_y_continuous(breaks = c(0, 5, 10, 15),
                     labels = c("0", "5", "10", "15+")) +
  labs(x = "", y = "Number of covariates considered") +
  facet_grid(cols = vars(Parameter), switch = "x") +
  guides(shape = "none") +
  theme(legend.position = "bottom", 
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        strip.text = element_text(size = 12, family = "Helvetica"), 
        axis.title.y = element_text(size = 13, family = "Helvetica"), 
        axis.text = element_text(size = 12, family = "Helvetica"),
        legend.text = element_text(size = 12, family = "Helvetica"))

plot_covariateQuantity
ggsave(plot = plot_covariateQuantity, filename = "Figures/CovParamPlot.jpeg",
       width = 8, height = 4)
```

@@

ggsave(plot = covariatePatchwork, "Figures/CovariateSummary.png",
```

>>>>

  ggplot() +
  geom_col(aes(x = Year, y = Articles, fill = Group), colour = "white") +
  scale_fill_manual("",
                    limits = c("YES", "EstRemaining"),
                    labels = c("Included articles", 
                               "Estimated qualifying articles"),
                    values = c("#4D7668", "gray50")) +
  scale_y_continuous(expand = c(0,0), limits = c(0, 65)) +
  scale_x_continuous(#limits = seq(2004, 2023, 1),
                     breaks = seq(2004, 2023, 4),
                     labels = seq(2004, 2023, 4)) +
  labs(x = "", y = "Number of articles") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-10,-10,-5,-10),
        legend.position = "top", 
        legend.key.size = unit(10, 'points'),
        legend.direction = "vertical",
        axis.text.y = element_text(size = 8, family = "helvetica", colour = "#585858"),
        axis.text.x = element_text(size = 8, family = "helvetica", 
                                   colour = "#585858", angle = 60,
                                   vjust = 1, hjust = 1), 
        axis.title = element_text(size = 8, family = "helvetica", colour = "#585858"), 
        legend.text = element_text(size = 8, family = "helvetica", colour = "#585858"),
        strip.text.x = element_text(size = 8, family = "helvetica", colour = "#585858"))
#+ facet_grid(cols = vars(Strata), scales = "free_x", switch = "x")
plot_reviewCoverage
ggsave(plot = plot_reviewCoverage, "Figures/CoveragePlot.png",
       width = 945, height = 700, units = "px")
```

@@

sheet_Objectives |>
  separate_longer_delim(`Authorship categories`, delim = ", ") |>
  summarise(nPer = n(),
            .by = `Review ID`) |>
  summarise(AffilCount = n(),
            .by = nPer)

@@

  ggplot(aes(x = Category, y = Covariates)) +
  geom_boxplot(aes(fill = Category), 
               outliers = TRUE, linewidth = .3, staplewidth = 0.33,
               colour = "gray25") +
  scale_fill_manual("", labels = c("Environmental covariates", "Structural covariates"),
                    values = c("#4D7668", "plum4")) +
  scale_colour_manual("", labels = c("Environmental covariates", 
                                     "Structural covariates"),
                      values = c("#4D7668", "plum4")) +
  scale_y_continuous(breaks = c(0, 5, 10, 15),
                     labels = c("0", "5", "10", "15+")) +
  labs(x = "", y = "Number of covariates\nconsidered") +
  facet_grid(cols = vars(Parameter), switch = "x") +
  guides(shape = "none") +
  theme(legend.position = "top",
        legend.box.margin = margin(-5,-10,-10,-10),
        legend.key.size = unit(12.5, 'points'),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(), 
        panel.grid.minor.y = element_blank(),
        #panel.background = element_rect(fill = "gray80"),
        strip.text = element_text(size = 7.5, family = "Helvetica", colour = "#585858"), 
        axis.title.y = element_text(size = 8, family = "Helvetica", colour = "#585858"), 
        axis.text = element_text(size = 8, family = "Helvetica", colour = "#585858"),
        legend.text = element_text(size = 8, family = "Helvetica", colour = "#585858"))

plot_covariateQuantity
ggsave(plot = plot_covariateQuantity, filename = "Figures/CovParamPlot.png",
       width = 1476, height = 700, units = "px")
```

@@

ggsave(plot = covariatePatchwork, "Figures/CovariateSummary.png")
```
